Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish

### 2024-10-02 manuscript.tex

The second, $f^c$ is normalized relative to the size of each cluster and can be considered the distribution of features in each cluster. It is useful for comparing the composition of each cluster relative to the features. For example, for $p=4$, if $f^c_{1j} = (0.4, 0.4, 0.1, 0.1)$ it suggests that high values (1's) of features 1 and 2 distinguish cluster 1. In the context of the later examples, this would mean cluster 1 contains tourists that list engaging in activities 1 and 2 but not 3 and 4. This normalisation produces what is called the {\bf intra-cluster fraction}.

The last, $f_f$ is normalized relative to each feature, which can be considered to be the distribution of clusters on each feature. It is useful to examine how features are related to a cluster. Considering the last metric, for example, if $f^f_{i1} = (0.5, 0.4, 0, 0.1, 0)$ ($k=5$) would indicate that high values on feature 1 primarily are in clusters 1, 2. In the context of the later examples, this would mean activity 1 is commonly listed only in clusters 1 and 2. This normalisation produces what is called the {\bf intra-feature fraction}.

>>>>

The second, $f^c$ is normalized relative to the size of each cluster and can be considered the distribution of features in each cluster. It is useful for comparing the composition of each cluster relative to the features. For example, for $p=4$, if $f^c_{1j} = (0.4, 0.4, 0.1, 0.1)$ it suggests that high values (1's) of features 1 and 2 distinguish cluster 1. In the context of the later examples, this would mean cluster 1 contains tourists that list engaging in activities 1 and 2 but not 3 and 4. This normalisation produces what is called the {\bf intra-cluster fraction}. \textcolor{red}{It corresponds to the cluster means. XXX why not larger values in the example, the maximum would be 1 so 0.4 still seems very moderate.}

The last, $f^f$ is normalized relative to each feature, which can be considered to be the distribution of clusters on each feature. It is useful to examine how features are related to a cluster. Considering the last metric, for example, if $f^f_{i1} = (0.5, 0.4, 0, 0.1, 0)$ ($k=5$) would indicate that high values on feature 1 primarily are in clusters 1, 2. In the context of the later examples, this would mean activity 1 is commonly listed only in clusters 1 and 2. This normalisation produces what is called the {\bf intra-feature fraction}. \textcolor{red}{Note that this must be interpreted with care in case of inbalanced cluster sizes.}
